---
title: "gun control chi-square"
author: "Juan Espinoza"
date: "November 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This: I'm Juan and I'm updating this markdown file here.

```{r}
library(tidyverse)
gc_df <- read_csv("gc_df.csv")
```

we are asking: is there a significant difference in recommended gun control action for male ande female respondents (should guns be easier, harder, or the same difficulty to get)? 1


Hey Juan, how is it going? :) 


Juan: Data wrangling and counts

chi sqaure: are proportions across groups so different that there is a significant difference

```{r}
get_guns <- gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender)

rownames(get_guns) <- c("Female", "Male")
```

My name is Fernanda the collaborator and I am going to be doing chi-square for independence.

Whe ask: "Is there a significant association between sex and opinion on wheter guns should be more difficult, easier, or the same difficulty to get?"

```{r}
#Let's look at the actual proportions. 

guns_prop <- prop.table(as.matrix(get_guns), 1)

guns_prop  

#Run a chi-square test for independence

guns_x2 <- chisq.test(get_guns)
guns_x2
  
```

"Recommended goverment actino on gun access differed significantly between male (n=) and female (n=) respondents ($\chi^2$(`r guns_x2$parameter`) =......, p < 0.001). Notably, a much higher proportion of female respondentes (57.4%) recommend making it more difficult to get guns, compare to 40.4% for male respondents."

```{r}

```

